\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=0.75in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}

\raggedright

% Define custom section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

% Set itemize to use less spacing
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}


\newcommand{\contact}[7]{
    \begin{center}
        \textbf{\LARGE #1} \\
        \vspace{0.1cm}
        \begin{tabular}{c}
            #2 \, | \, #3 \, | \, \href{mailto:#4}{#4}
        \end{tabular} \\
        \vspace{0.1cm}
        \small
        \begin{tabular}{ccc}
            \href{#5}{LinkedIn}: \texttt{#5} & \href{#6}{GitHub}: \texttt{#6} & \href{#7}{Blog}: \texttt{#7}
        \end{tabular}
    \end{center}
    \vspace{-0.4cm} % Adjust vertical space
    \begin{itemize}[leftmargin=0.5cm]
        \item Experienced in creating high quality pull requests with solid software design and test coverage under continuous integration and code review workflow.
        \item Proficient in project management, collaboration, technical communication and documentation.
        \item Demonstrated adaptability in swiftly acquiring and applying new concepts independently.
    \end{itemize}
}

\begin{document}

% Contact Information
\contact{\color{NavyBlue}Raine Yang}{\color{NavyBlue}Toronto, ON}{+1 (437) 376-1066}{raine.yang@mail.utoronto.ca}{linkedin.com/in/raine-yang/}{github.com/Raine-Yang-UofT}{raineyang.hashnode.dev/}

% Education
\section*{\color{NavyBlue}Education}
\textbf{Computer Science Specialist ASIP Program \& Math Minor} \\
\textbf{University of Toronto - Victoria College} \\
\textit{09/2023 - Present} \textit{\textbf{GPA: 4.0}} \\
\noindent
\begin{minipage}[t]{0.5\textwidth}
\subsection*{Relevant Courses:}
\begin{itemize}[leftmargin=0.7cm, labelsep=0.5cm]
    \item Software Design
    \item Computer Organization
    \item Theory of Computation
\end{itemize}
\end{minipage}%
\noindent
\begin{minipage}[t]{0.5\textwidth}
\subsection*{Awards:}
\begin{itemize}[leftmargin=0.7cm, labelsep=0.5cm]
    \item University of Toronto Scholar
    \item The Mary Mounfield Scholarship
    \item Clifton Graham Roberts Admission Award
\end{itemize}
\end{minipage}

\vspace{0.1cm}

% Work Experience
\begin{multicols}{2}
\noindent
\section*{\color{NavyBlue}Work Experience}

\textbf{\large{Software Developer}} \\
\textbf{Students Developing Software Team - University of Toronto} \\
\textit{05/2024 -- Present} \\
\begin{itemize}
    \item Contribute to \textbf{PythonTA} static code analysis tool used by thousands of first-year CS students at the University of Toronto through new features implementation, bug fixes, code refactoring, and test update. Ensured code quality and maintainability through standardized \textbf{continuous integration} and \textbf{code review} workflows.
    \item Effectively communicate project progress through weekly presentations and extensive documentation on technical blog, fostering team collaboration and knowledge sharing.
\end{itemize}

\vspace{0.25cm}

\noindent
\textbf{\large{Software Developer Intern}}\\
\textbf{RoboTerra} \\
\textit{08/2020 -- 08/2023} \\
\begin{itemize}
    \item Implemented a glass surface detection algorithm in \textbf{Python} and integrated it with \textbf{ROS} Gmapping to improve lidar mapping accuracy by 50\% in environments with glass or reflective walls.
    \item Designed a face-recognition-based light alarm clock using \textbf{Python's OpenCV} and textbf{Arduino}, establishing a distributed system via \textbf{ROS2}. Created a \textbf{SolidWorks} model for the prototype.
    \item Engineered API libraries for \textbf{Arduino} sensors, seamlessly integrating them into the company's backend repository, and provided detailed documentation for frontend development.
    \item Provided technical assistance for the Youth Silicon Valley AI Contest, including product repair, programming, and contest field maintenance.
\end{itemize}

\vspace{0.25cm}

\noindent
\textbf{\large{AP Computer Science A Instructor}} \\
\textbf{Xi'an Gaoxin No.1 High School} \\
\textit{05/2022 -- 01/2023} \\
\begin{itemize}
    \item Solely instructed a class of 25 grade 12 students in \textbf{Java programming} and \textbf{AP Computer Science A} at Xi’an Gaoxin No.1 High School.
\end{itemize}

\columnbreak

% Skills
\section*{\color{NavyBlue}Skills}
\noindent
\begin{tabular}{l|l|l|l|l}
\textbf{Python} & \textbf{C\#} & \textbf{Java} & \textbf{Rust} & \textbf{Arduino} \\
\end{tabular}

\vspace{0.3cm}

\noindent
\begin{tabular}{l|l|l|l}
\textbf{Unity} & \textbf{ROS/ROS2} & \textbf{Git} & \textbf{Linux} \\
\end{tabular}

% Personal Projects
\section*{\color{NavyBlue}Personal Projects}
\noindent
\textbf{Technical Blog Writing} \hfill \\
\textit{10/2020 -- Present} \\
\begin{itemize}
    \item Published \textbf{200+} technical blogs on \textbf{Hashnode} and \textbf{CSDN}, documenting problem-solving processes and self-taught topics. Garnered 20,000+ views and 300+ followers across platforms.
    \item Links: Hashnode (raineyang.hashnode.dev) CSDN (blog.csdn.net/Raine\_Yang).
\end{itemize}

\vspace{0.25cm}

\noindent
\textbf{Game Developer - University of Toronto Game Development Club} \\
\textit{02/2024 -- Present} \\
\begin{itemize}
    \item Lead the development of video game project \textit{What The Thunder Said} in \textbf{Unity} and \textbf{C\#}.
    \item Designed and implemented the comprehensive back-end architecture of the game system, applying \textbf{object-oriented design principles and patterns} to ensure scalability and maintainability, resulting in a robust foundation for future game updates and features.
\end{itemize}

\vspace{0.25cm}

\noindent
\textbf{Manhole Watchdog - IEEE New Hacks Hackathon} \\
\textit{11/2023} \\
\begin{itemize}
    \item Engineered an intelligent manhole monitoring system during \textbf{IEEE New Hacks Hackathorn}. Independently implemented the hardware for displacement and tilt detection using \textbf{Arduino} while orchestrating effective team collaboration to create a solution addressing misplaced, lost, or stolen manholes.
    \item Link: GitHub (github.com/Raine-Yang-UofT/New-Hacks-2023-Intelligent-Manhole)
\end{itemize}
\end{multicols}

\end{document}
